---
title: "Package_exTra"
output: html_document
date: "2025-05-19"
---

```{r setup, include=FALSE}
usethis::use_tidy_style(strict = TRUE)
```

```{r git_1, include=FALSE}
usethis::use_git()
```


```{r git_2, include=FALSE}
usethis::create_github_token()
```

```{r git_3, include=FALSE}
gitcreds::gitcreds_set() # Then enter the freshly generated token
```

```{r git_4, include=FALSE}
usethis::use_github()
```

```{r git_5, include=FALSE}
usethis::use_lifecycle()
```

usethis::use_tidy_github()
usethis::use_tidy_github_actions()
# overwrite tidy's default "check-full" with "check-standard"
# to not run so many checks
usethis::use_github_action("check-standard")
usethis::use_tidy_github_labels()
usethis::use_pkgdown_github_pages()


# non-git stuff further
usethis::use_author(
    given = "Gunther",
    family = "Glehr",
    email = "gunthergl@gmx.net",
    role = c("aut", "cre"),
    comment = c("ORCID" = "0000-0002-1495-9162")
)
usethis::use_news_md()
lintr::use_lintr(type = "tidyverse")
# Change manually to:
# linters: linters_with_defaults(line_length_linter = line_length_linter(120),indentation_linter = indentation_linter(4)) # see vignette("lintr")
# encoding: "UTF-8"

# Include all the relevant packages
usethis::use_package("flowWorkspace")
usethis::use_package("flowCore")
usethis::use_package("tibble")
usethis::use_package("dplyr")
usethis::use_package("xml2")
